Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw

\begin{abstract} 
abstract on separate page
100 - 150 words
\end{abstract}

@@

In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant. An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations. Regressing with the imputed dataset, results decrease by about 0.1. Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.

@@

In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant. For the original data set, the coeffiecent is slightly negative. Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations. This coefficent is as well insignifacant.

In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger. For the original data set, the OLS coefficent amounts to 0.27, which is highly significant. When using WLS, we find a slightly negative association. A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02. This coefficent is not significant. For the imputed dataset we find a similar picture.

@@

The partition approach partitions data into subsets of related features. It then  summarizes each subset into one new feature. By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}. A function g is implemented using the arithmetic mean. In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity. What is as well different is the information loss constraint. It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.

>>>>

\begin{abstract} 
This study presents the results of the analysis of the data of effects of the non-profit organisation 'CHILDREN for a better world ev'. We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables. We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus. 
\end{abstract}

@@

In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant. An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations. Regressing with the imputed dataset, results decrease by about 0.1. Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore. Regressing with the imputed data set with extracted factor scores as controls, we still obtain a slightly postive significant coefficent: An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.18 standard deviations. Overall, there is a positive association between the two variables.

@@

In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant. For the original data set, the coeffiecent is slightly negative. Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations. This coefficent is as well insignifacant. Also, regressing with the imputed data set with extracted factor scores as controls, does not display a profound connection between beneficiaries dietary knowledge and the healthy meals index.

In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger. For the original data set, the OLS coefficent amounts to 0.27, which is highly significant. When using WLS, we find a slightly negative association. A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02. This coefficent is not significant. For the imputed dataset we find a similar picture. Similary to the previous regression, the imputed data set with extracted factor scores as controls, does not show any association between the appreciation of a healthy diet and the healthy meals index.

@@

The partition approach partitions data into subsets of related features. It then  summarizes each subset into one new feature. By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}. The function is implemented using the arithmetic mean. In contrast to methods like the factor analysis, if a feature is identified to be related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity. What is as well different is the information loss constraint. It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
